### 2020-03-23 Strings2020/strings2/strings2.tex
Finalize strings2, update advqft2

\newcommand{\hwNumber}{2 [WIP]}

@@

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}
\usepackage{cancel}

@@

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}
	\begin{enumerate}
	\item \textbf{BRST Quantization of Bosonic String}: 
	\begin{gather}
		S = S^X + S^{bc},\\
		S^X = - \frac{1}{2\pi\alpha'} \int\dd[2]{z}
			\pd X^\mu \pdbar X_\mu,\quad
		S^{bc} = \frac{1}{2\pi} \int\dd[2]{z}
			\pqty\Big{
				b\,\pdbar c
				+ \tilde{b}\,\pd\tilde{c}
			}
	\end{gather}
	This is the gauge fixed action. The corresponding BRST transformation is listed in \textit{Polchinski}; for each of the subsystems, we have its (classical) energy-momentum:
	\begin{equation}
		T^X(z)
		= - \frac{1}{\alpha'}\,
			\normorder{\pd X^\mu \pd X_\mu}\,,\quad
		\tilde{T}^X(\bar{z})
		= - \frac{1}{\alpha'}\,
			\normorder{\pdbar X^\mu \pdbar X_\mu}\,,
		\\[.5ex]
		T^{bc}(z) = \normorder{(\pd b)\,c}
			- 2\,\pd(\normorder{bc}),\quad
		\tilde{T}^{bc}(\bar{z}) = \normorder{
			(\pdbar \tilde{b})\,\tilde{c}
		} - 2\,\pdbar(\normorder{
			\tilde{b}\tilde{c}
		}),
	\end{equation}

@@

	The transformation of $b,c$ is less obvious; for holomorphic current, we need only focus on the holomorphic part of $S^{bc}$; on-shell variation yields:
	\begin{equation}
		0 = \var{S}^{bc}
		= \pqty{\frac{1}{2\pi} \int \dd[2]{z} \pqty{
			- \pdbar c\,\var{b}
			- \pdbar b\,\var{c}
		}}_{\!\!=\mspace{1mu}0}
		+ \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar\epsilon\,\pqty\big{
				-ibc\,\pd c
			} 
	\end{equation}
	Here we've plugged in $
		\var{c} = i\epsilon(z,\bar{z})\,c\pd c
	$, and we have moved $\pdbar\epsilon$ to the beginning of the expression, while respecting the anti-commuting nature of $\epsilon$. With a conventional $i$ coefficent (which agrees with the convention of $j^X$), we have $bc$'s contribution to the conserved current:
	\begin{equation}
		j^{bc} = i\,\pqty\big{
			-ibc\,\pd c
		} = bc\,\pd c
	\end{equation}

	Note that $j^{bc}$ is, in fact, related to the energy-momentum (at least classically):
	\begin{equation}
		\frac{1}{2}\,cT^{bc}
		= \frac{1}{2}\,c\,{(\pd b)\,c}
			- c\,\pd({bc})
		= - c\,\pd({bc})
		= - cb\,\pd c
		= bc\,\pd c = j^{bc}
	\end{equation}
	Hence we have the classical BRST current:
	\begin{equation}
		j(z) = c(z)\,\pqty{
			T^X + \frac{1}{2}\,T^{bc}
		}
	\end{equation}

@@

		\sim \eqref{eq:BRST_Tj_OPE_partI}

@@

	We see that $j(z)$ defined with na\"ive normal ordering is \textit{almost} but \textit{not quite} a primary. It differs from primary OPE at $\order{\frac{1}{z^4}}$ and $\order{\frac{1}{z^3}}$. However, it is possible to make it into a primary by adding extra terms that do not interfere with current conservation $\pdbar j = 0$. To cancel the $\frac{3}{z^3}\,\pd c(0)$ term, notice that $
		b(z)\,\pd^2 c(0) \sim \frac{2}{z^3}
	$, therefore it may be helpful to look at:
	\begin{equation}
	\begin{aligned}
		T(z)\,\pd^2 c(0)
		\sim T^{bc}(z)\,\pd^2 c(0)
		&\sim \pd^2_w \pqty{
			T^{bc}(z)\,c(w)
		}_{w\to 0} \\
		&\sim \pd^2_w \pqty{
			\frac{-1}{(z-w)^2}\,c(w)
			+ \frac{1}{z-w}\,\pd c(w)
		}_{\!w\to 0} \\[.5ex]
		&\sim \frac{-12}{2z^4}\,c(0)
			+ \frac{-2}{z^3}\,\pd c(0)
			+ \frac{1}{z^2}\,\pd^2 c(0)
			+ \frac{1}{z}\,\pd^3 c(0),
	\end{aligned}
	\end{equation}
	Again we've used $Tc$ OPE of the primary $c(w)$. We see that indeed, the $\frac{1}{z^3}\,\pd c(0)$ term can be canceled by shifting $j(z)$:
	\begin{gather}
		j(z)\ \longmapsto\ j(z)
			+ \frac{3}{2}\,\pd^2 c(z),\quad
		j(z) = j^X + j^{bc}
			+ \frac{3}{2}\,\pd^2 c,\\[1ex]
		T(z)\,j(0)
		\sim \frac{D-26}{2z^4}\,c(0)
			+ \frac{1}{z^2}\,j(0)
			+ \frac{1}{z}\,\pd j(0),
	\end{gather}

	We see that $j(z)$ defined in this way is a primary of weight $(1,0)$ in $D = 26$. This is the quantum BRST current. 
	\qedfull

@@

	\item

@@

	\clearpage

	\quad
	\vfill\pagebreak

	\item \textbf{Spinning Closed String in AdS Space}:

	For a classical spinning string, we have Nambu--Goto action:
	\begin{equation}
		S_{NG}
		= -T \int \dd{\tau} \dd{\sigma}
			\sqrt{-\det \gamma_{ab}},\quad
		\gamma_{ab} = G_{\mu\nu}
			\pdd{a}X^\mu \pdd{b}X^\nu
	\end{equation}
	Here $G_{\mu\nu}$ is the spacetime metric. $\gamma_{ab}$ can be treated as the induced metric on the worldsheet.

	In AdS space we have:
	\begin{equation}
		ds^2
		= R^2\pqty{
			- \sqcosh\rho \dd{t}^2
			+ \dd{\rho}^2
			+ \sqsinh\rho \dd{\Omega}^2
		}
	\end{equation}
	Where $\dd{\Omega}^2$ is the metric of a unit $(d-2)$--sphere $S^{d-2}$. For convenience let's define unit $S^{d-2}$ metric $G^1_{ij}$, and raise or lower the $i,j,\cdots$ indices using $G^1_{ij}$ instead of $G_{ij}$, i.e.,
	\begin{equation}
		G^1_{ij} = G_{ij} /\,\pqty{
			R^2 \sqsinh\rho
		},\quad
		i,j = 2,\cdots,d-1
	\end{equation}

	Furthermore, we consider the special case that the closed string is \textit{folded}, like a rubber band stretched along a line; in this case we can choose the worldsheet parameter $(\tau,\sigma) = (t,\rho)$ while $\Omega = \Omega(t,\rho) = \Omega(\tau,\sigma)$, which leads to the following decomposition:
	\begin{align}
		\pdd{a} X^\mu
		&= \delta^\mu_a + \delta^\mu_i\,
			\pdd{a}\Omega^i,\quad
			a = 0,1,\quad
			i = 2,\cdots,d-1,\\[.5ex]
		\gamma_{ab}
		&= G_{\mu\nu}\,
			\pdd{a}X^\mu \pdd{b}X^\nu
		\notag\\
		&= G_{ab} + G_{ij}\,
			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
		\notag\\
		&= G_{ab} + R^2\sqsinh\rho\,G^1_{ij}\,
			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
		\notag\\
		&= R^2\Bqty{\mat{
			-\sqcosh\rho & \\
			& 1 \\
		} + \sqsinh\rho\,\mat{
			(\pdd{a}\Omega)^2 &
			\pdd{a}\Omega\cdot\pdd{b}\Omega \\
			\pdd{b}\Omega\cdot\pdd{a}\Omega &
			(\pdd{b}\Omega)^2 \\
		}}
%		\notag\\
%		&= R^2\,\sqsinh\rho\,\Bqty{\mat{
%			-\oppower{\coth}{2}\rho & \\
%			& \oppower{\csch}{2}\rho \\
%		} + \,\mat{
%			(\pdd{a}\Omega)^2 &
%			\pdd{a}\Omega\cdot\pdd{b}\Omega \\
%			\pdd{b}\Omega\cdot\pdd{a}\Omega &
%			(\pdd{b}\Omega)^2 \\
%		}}
	\end{align}
	Here $
		\pdd{a}\Omega\cdot\pdd{b}\Omega
		\equiv \pdd{a}\Omega^i\,\pdd{b}\Omega_i
		\equiv G^1_{ij}\,
			\pdd{a}\Omega^i\,\pdd{b}\Omega^j
	$, and we have:
	\begin{equation}
	\begin{aligned}
		\det \gamma_{ab}
		&= (R^2)^2\,\Big\{
			\oppower{\sinh}{4}\rho\,
			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
		\\
		&\qquad\qquad\qquad
			+ \oppower{\sinh}{2}\rho\,\pqty{
				(\pdd{a}\Omega)^2
				- (\pdd{b}\Omega)^2
				\oppower{\cosh}{2}\rho
			}
		\\
		&\qquad\qquad\qquad
			- \oppower{\cosh}{2}\rho\,
		\Big\},\\[.5ex]
		\sqrt{-\det \gamma_{ab}}
		&= R^2\,\Big\{
			\oppower{\cosh}{2}\rho
			- \oppower{\sinh}{2}\rho\,\pqty{
				(\pdd{a}\Omega)^2
				- (\pdd{b}\Omega)^2
				\oppower{\cosh}{2}\rho
			}
		\\[-.5ex]
		&\qquad\qquad\quad
			- \oppower{\sinh}{4}\rho\,
			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
		\Big\}^{\!1/2}
	\end{aligned}
	\end{equation}

	Mark the end points of the string with $\rho = r(t)$, then the total length of such closed folded string is $\ell = 4r$. We then have:
	\begin{equation}
		S = -4TR^2 \int\dd{t} \int_0^r \dd{\rho}
		\sqrt{
			\oppower{\cosh}{2}\rho
			- \oppower{\sinh}{2}\rho\,\pqty{
				(\pdd{a}\Omega)^2
				- (\pdd{b}\Omega)^2
				\oppower{\cosh}{2}\rho
			}
			- \oppower{\sinh}{4}\rho\,
			\det\,(\pdd{a}\Omega^i\pdd{b}\Omega_i)
		}
	\end{equation}
\pagebreak[3]

>>>>

\newcommand{\hwNumber}{2}

@@

\newcommand{\Vir}{\mathbf{V}\mfrak{ir}}

@@

%{
%	\noindent\itshape%
%	本文约定：度规$\eta\sim\pqty{-,+,+,+}$, 指标$\mu,\nu,\dots = 0,1,2,3,\ i,j,\dots = 1,2,3$.
%}

	\begin{enumerate}
	\item \textbf{BRST Quantization of Bosonic String}: 
	\begin{gather}
		S = S^X + S^{bc},\\
		S^X = \frac{1}{2\pi\alpha'} \int\dd[2]{z}
			\pd X^\mu \pdbar X_\mu,\quad
		S^{bc} = \frac{1}{2\pi} \int\dd[2]{z}
			\pqty\Big{
				b\,\pdbar c
				+ \tilde{b}\,\pd\tilde{c}
			}
	\end{gather}
	This is the gauge fixed action. The corresponding BRST transformation is listed in \textit{Polchinski}; for each of the subsystems, we have its energy-momentum:
	\begin{gather}
		T^X(z)
		= - \frac{1}{\alpha'}\,
			\normorder{\pd X^\mu \pd X_\mu}\,,\quad
		\tilde{T}^X(\bar{z})
		= - \frac{1}{\alpha'}\,
			\normorder{\pdbar X^\mu \pdbar X_\mu}\,,
		\\[.5ex]
		T^{bc}(z) = \normorder{(\pd b)\,c}
			- 2\,\pd(\normorder{bc}),\quad
		\tilde{T}^{bc}(\bar{z}) = \normorder{
			(\pdbar \tilde{b})\,\tilde{c}
		} - 2\,\pdbar(\normorder{
			\tilde{b}\tilde{c}
		}),
	\end{gather}

@@

	The transformation of $b,c$ is less obvious; for holomorphic current, we need only focus on the holomorphic part of $S^{bc}$; on-shell variation yields:
	\begin{equation}
		0 = \var{S}^{bc}
		= \pqty{\frac{1}{2\pi} \int \dd[2]{z} \pqty{
			- \pdbar c\,\var{b}
			- \pdbar b\,\var{c}
		}}_{\!\!=\mspace{1mu}0}
		+ \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar \pqty{b\var{c}}
		= \frac{1}{2\pi} \int \dd[2]{z}
			\pdbar\epsilon\,\pqty\big{
				-ibc\,\pd c
			} 
	\end{equation}
	Here we've plugged in $
		\var{c} = i\epsilon(z,\bar{z})\,c\pd c
	$, and we have moved $\pdbar\epsilon$ to the beginning of the expression, while respecting the anti-commuting nature of $\epsilon$. With a conventional $i$ coefficient (which agrees with the convention of $j^X$), we have $bc$'s contribution to the conserved current:
	\begin{equation}
		j^{bc} = i\,\pqty\big{
			-ibc\,\pd c
		} = bc\,\pd c
	\end{equation}

	Note that $j^{bc}$ is, in fact, related to the energy-momentum (at least classically):
	\begin{equation}
		\frac{1}{2}\,cT^{bc}
		= \frac{1}{2}\,c\,{(\pd b)\,c}
			- c\,\pd({bc})
		= - c\,\pd({bc})
		= - cb\,\pd c
		= bc\,\pd c = j^{bc}
	\end{equation}
	Hence we have the classical BRST current:
	\begin{equation}
		j(z) = c(z)\,\pqty{
			T^X + \frac{1}{2}\,T^{bc}
		}
	\end{equation}
	\vspace*{-1.5\baselineskip}

	\qed

@@

		\sim \pqty\big{
			\eqref{eq:BRST_Tj_OPE_partI}

@@

	We see that $j(z)$ defined with na\"ive normal ordering is \textit{almost} but \textit{not quite} a primary. It differs from primary OPE at $\order{\frac{1}{z^4}}$ and $\order{\frac{1}{z^3}}$. However, it is possible to make it into a primary by adding extra terms that do not interfere with current conservation $\pdbar j = 0$. To cancel the $\frac{3}{z^3}\,\pd c(0)$ term, notice that $
		b(z)\,\pd^2 c(0) \sim \frac{2}{z^3}
	$, therefore it may be helpful to look at:
	\begin{equation}
	\begin{aligned}
		T(z)\,\pd^2 c(0)
		\sim T^{bc}(z)\,\pd^2 c(0)
		&\sim \pd^2_w \pqty{
			T^{bc}(z)\,c(w)
		}_{w\to 0} \\
		&\sim \pd^2_w \pqty{
			\frac{-1}{(z-w)^2}\,c(w)
			+ \frac{1}{z-w}\,\pd c(w)
		}_{\!w\to 0} \\[.5ex]
		&\sim \frac{-12}{2z^4}\,c(0)
			+ \frac{-2}{z^3}\,\pd c(0)
			+ \frac{1}{z^2}\,\pd^2 c(0)
			+ \frac{1}{z}\,\pd^3 c(0),
	\end{aligned}
	\label{eq:BRST_Td2c_OPE}
	\end{equation}
	Again we've used $Tc$ OPE of the primary $c(w)$. We see that indeed, the $\frac{1}{z^3}\,\pd c(0)$ term can be canceled by shifting $j(z)$:
	\begin{gather}
		j(z)\ \longmapsto\ j(z)
			+ \frac{3}{2}\,\pd^2 c(z),\quad
		j(z) = cT^X + \normorder{bc\,\pd c}
			+ \frac{3}{2}\,\pd^2 c,\\[1ex]
		T(z)\,j(0)
		\sim \frac{D-26}{2z^4}\,c(0)
			+ \frac{1}{z^2}\,j(0)
			+ \frac{1}{z}\,\pd j(0),
	\end{gather}

	We see that $j(z)$ defined in this way is a primary of weight $(1,0)$ in $D = 26$. This is the quantum BRST current. 
	\qed

@@

	\item For $jj$ OPE, we have:
	\begin{gather}
		j = cT^X + j',\quad
		j' \equiv j^{bc}
			+ \frac{3}{2}\,\pd^2 c,\quad
		j^{bc}
		= \frac{1}{2}\normorder{cT^{bc}}
		= \normorder{bc\,\pd c}\,,\\[1ex]
%		
%		j = \frac{1}{2}\,cT^X
%			+ \frac{1}{2}\,\normorder{cT}
%			+ \frac{3}{2}\,\pd^2 c,\\
%
	\begin{aligned}
		j_z j_0
		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
			+ \normorder{\Bqty{c_z j'_0}\,T^X_z}
			+ \normorder{\Bqty{j'_z c_0}\,T^X_0}
			+ {j'_z j'_0} \\[.5ex]
		&\sim \normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
			+ \normorder{\Bqty{c_z j^{bc}_0}\,T^X_z}
			+ \normorder{\Bqty{j^{bc}_z c_0}\,T^X_0}
			+ {j'_z j'_0}\,,
	\end{aligned}
	\end{gather}
	From now on, for convenience and clarity, we will use subscripts to denote variable dependence: $c_z = c(z)$. Let's compute this term by term. We have:
	\begin{align}
		\normorder{\Bqty{T^X_z T^X_0}\,c_z c_0}
		&\sim \normorder{\pqty{
			\frac{D}{2z^4}
			+ \frac{2}{z^2}\,{T^X_0}
			+ \frac{1}{z}\,{\pd T^X_0}
		}\pqty{
			z\,\pd c_0
			+ \frac{z^2}{2}\,\pd^2 c_0
			+ \frac{z^3}{6}\,\pd^3 c_0
		} c_0} \notag\\
		&\sim -\pqty{
			\frac{D}{2z^3}\,c\,\pd c_0
			+ \frac{D}{4z^2}\,c\,\pd^2 c_0
			+ \frac{D}{12z}\,c\,\pd^3 c_0
			+ \frac{2}{z}\,\normorder{T^X c\,\pd c_0}
		}, 
		\label{eq:BRST_TTcc_OPE} \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		jc OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
		j^{bc}_z c_0
		&\sim \frac{1}{2}\,
			\normorder{cT^{bc}}_{\,z}\,c_0
		\sim \frac{1}{2}\,c_z \Bqty{
			\normorder{T^{bc}}_{\,z}\,c_0
		}
		\sim \frac{1}{2}\,c_z \Bqty{
			T_z\,c_0
		} \notag\\
		&\sim -\frac{1}{2}\,\pqty{
			\frac{-1}{z^2}\,c_0
			+ \frac{1}{z}\,\pd c_0
		}\pqty\big{
			c_0 + z\,\pd c_0
		} \sim 0, \\
		j^{bc}_0 c_z
		&\sim 0,
	\end{align}
	\begin{equation}
	\begin{aligned}
		j'_z j'_0
		&\sim j^{bc}_z j^{bc}_0
			+ \frac{3}{2}\,j^{bc}_z\,\pd^2 c_0
			+ \frac{3}{2}\,\pd^2 c_z\,j^{bc}_0 \\
		&\sim \frac{1}{2}\,
			\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
		+ \frac{3}{2}\,\pqty{
			j^{bc}_z\,\pd^2 c_0
			+ \pd^2 c_z\,j^{bc}_0
		},
	\end{aligned}
	\end{equation}

	The task is now reduced to calculating terms in the above $j'j'$ OPE, which can be laboriously computed following a similar procedure as before. Note that there will be a $
		\frac{1}{z}\,\normorder{cT^{bc}}\,\pd c_0
	$ term which combines with the $
		\frac{2}{z}\,\normorder{cT^{X}}\,\pd c_0
	$ term in \eqref{eq:BRST_TTcc_OPE}. In total, we obtain the final $jj$ OPE:
	\begin{equation}
		j_z j_0
		\sim - \frac{D-18}{2z^3}\,c\,\pd c_0
			- \frac{D-18}{4z^2}\,c\,\pd^2 c_0
			- \frac{D-26}{12z}\,c\,\pd^3 c_0
	\end{equation}

%	For the first term, we have:
%	\begin{equation}
%	\begin{aligned}
%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
%		&\sim \normorder{\wick{
%			\c1 c T^{bc}_z \c1 j^{bc}_0
%		}} + \normorder{\wick{
%			c \c1 T^{bc}_z \c1 j^{bc}_0
%		}} + \normorder{\wick{
%			\bcontraction[1.1ex]{c}{T}{^{bc}_z}{j}
%			\c1 c T^{bc}_z \c1 j^{bc}_0
%		}} \\[.5ex]
%		&\sim \frac{1}{z}\,(+1)\,\normorder{
%			T^{bc}_z c\,\pd c_0
%		} + \normorder{c_z \Bqty{
%			\eqref{eq:BRST_Tj_OPE_partIII}
%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
%			\Bqty{T^{bc}_z c_0}\,\pd c_0
%			+ (+1)\,
%				c_0\,\Bqty{T^{bc}_z\,\pd c_0}
%		}} \\
%		&\sim \frac{1}{z}\,\normorder{
%			T^{bc} c\,\pd c_0
%		} + \normorder{c_z \Bqty{
%			\eqref{eq:BRST_Tj_OPE_partIII}
%		}} + \frac{1}{z}\,\normorder{\pqty\Big{
%			\Bqty{T^{bc}_z c_0}\,\pd c_0
%			+ c_0\,\Bqty{T^{bc}_z\,\pd c_0}
%		}}
%	\end{aligned}
%	\end{equation}
%	Here we've used the fact that there is only one $b$ in $T^{bc}$, hence all non-singular are accounted for in the above expression. Note again that $c$ is primary; similar to \eqref{eq:BRST_Td2c_OPE}, we have:
%	\begin{equation}
%	\begin{aligned}
%		\normorder{cT^{bc}}_{\,z}\,j^{bc}_0
%		&\sim \normorder{\pqty{
%			c_0 + z\,\pd c_0
%			+ \frac{z^2}{2}\,\pd^2 c_0
%			+ \frac{z^3}{6}\,\pd^3 c_0
%		} \pqty{
%			\frac{-4}{z^4}\,c_0
%			+ \frac{3}{z^3}\,\pd c_0
%			+ \frac{1}{z^2}\,j^{bc}_0
%			+ \frac{1}{z}\,\pd j^{bc}_0,
%		}} \\
%		&\qquad + \frac{1}{z}\,\pqty{
%			\frac{-1}{z^2}\,c\,\pd c_0
%			+ c_0\cdot\frac{1}{z}\,\pd^2 c_0
%		} \\
%		&\sim \frac{3+4-1}{z^3}\,c\,\pd c_0
%			+ \frac{4/2+1}{z^2}\,c\,\pd^2 c_0
%			+ \frac{4/6}{z}\,c\,\pd^3 c_0 \\
%	\end{aligned}
%	\end{equation}
%	
%	
%	\begin{align}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		j^{bc}_z\,\pd^2 c_0
%		&\sim \frac{1}{2}\,c_z\,\Bqty{
%			T^{bc}_z\,\pd^2 c_0
%		} \\
%		\sim\eqref{eq:BRST_Td2c_OPE}
%		&\sim \frac{1}{2}\,c_z\,\pqty{
%			\frac{-6}{z^4}\,c_0
%			+ \frac{-2}{z^3}\,\pd c_0
%			+ \frac{1}{z^2}\,\pd^2 c_0
%			+ \frac{1}{z}\,\pd^3 c_0
%		} \\
%		\sim (\textsl{Taylor})
%		&\sim \frac{1}{2}\,\pqty{
%			\frac{6-2}{z^3}\,
%				c_0\,\pd c_0
%			+ \frac{6/2+1}{z^2}\,
%				c_0\,\pd^2 c_0
%			+ \frac{6/6+1}{z}\,
%				c_0\,\pd^3 c_0
%		} \\
%		&\sim \frac{1}{2}\,\pqty{
%			\frac{4}{z^3}\,
%				c_0\,\pd c_0
%			+ \frac{4}{z^2}\,
%				c_0\,\pd^2 c_0
%			+ \frac{2}{z}\,
%				c_0\,\pd^3 c_0
%		} \\[2ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%%		ANOTHER OPE ...
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\pd^2 c_z\,j^{bc}_0
%		&\sim -j^{bc}_0\,\pd^2 c_z \\
%		&\sim - \frac{1}{2}\,c_0\,\Bqty{
%			T^{bc}_0\,\pd^2 c_z
%		} \\
%		\sim\eqref{eq:BRST_Td2c_OPE}
%		&\sim -\frac{1}{2}\,c_0\,\pqty{
%			\frac{-2}{(-z)^3}\,\pd c_z
%			+ \frac{1}{(-z)^2}\,\pd^2 c_z
%			+ \frac{1}{-z}\,\pd^3 c_z
%		} \\
%		&\sim -\frac{1}{2}\,c_0\,\pqty{
%			\frac{2}{z^3}\,\pd c_z
%			+ \frac{1}{z^2}\,\pd^2 c_z
%			+ \frac{-1}{z}\,\pd^3 c_z
%		} \\
%		\sim (\textsl{Taylor})
%		&\sim -\frac{1}{2}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{1+2}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{-1+1+1}{z}\,c_0\,\pd^3 c_0
%		} \\
%		&\sim -\frac{1}{2}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{3}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
%		} \\[1ex]
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
%		\frac{3}{2}\,\pqty{
%			j^{bc}_z\,\pd^2 c_0
%			+ \pd^2 c_z\,j^{bc}_0
%		} &\sim \frac{3}{4}\,\pqty{
%			\frac{2}{z^3}\,c_0\,\pd c_0
%			+ \frac{1}{z^2}\,c_0\,\pd^2 c_0
%			+ \frac{1}{z}\,c_0\,\pd^3 c_0
%		}
%	\end{align}

	\item Following the convention of \textit{Polchinski}, expand $X^\mu,b,c$ into modes $\alpha^\mu_n,b_n,c_n$, then a generic level 2 state of an open string can be created as\footnote{
		Reference: Bram M.~Wouters, \href{https://esc.fnwi.uva.nl/thesis/centraal/files/f1989820784.pdf}{\textit{BRST quantization and string theory spectra}}. 
	}:
	\begin{equation}
	\begin{aligned}
		\ket{\psi} = \big(
			&e_{\mu\nu}
				\alpha^\mu_{-1}
				\alpha^\nu_{-1}
			+ \beta_\mu
				\alpha^\mu_{-1} b_{-1}
			+ \gamma_\mu
				\alpha^\mu_{-1} c_{-1}
			\\ &\qquad
			+ \eta\,b_{-1} c_{-1}
			+ e_\mu \alpha^\mu_{-2}
			+ \beta\,b_{-2}
			+ \gamma\,c_{-2}
		\big)\,\ket{k;0}
	\end{aligned}
	\end{equation}
	Here $e_{\mu\nu}$ is chosen to be symmetric since $
		\alpha^\mu_{-1}
		\alpha^\nu_{-1}
	$ commutes. 
	By acting on $L_0$ (expanded in modes), we find that $
		m^2 = -k^2 = \frac{1}{\alpha'}
	$: massive.

	The BRST charge $
		Q = \frac{1}{2\pi i} \oint \pqty{
			\dd{z} j(z)
			- \dd{\bar{z}} \tilde{j}(z)
		}
	$ can also be expanded in modes; the physical states are firstly, $Q$-closed; i.e.
	\begin{equation}
		Q_B \ket{\psi} = 0
		\ \Longrightarrow\ %
		k^\mu e_{\mu\nu} = 0,\quad
		k^\mu e_\mu = 0,\quad
		\beta_\mu = \beta = 0,
	\end{equation}
	This is also the negative-norm states.

	On the other hand, $Q$-exact states generate gauge transformations; this gives:
	\begin{equation}
		\gamma_\nu
		\mapsto \gamma_\nu + k^\mu e_{\mu\nu},\quad
		\gamma
		\mapsto \gamma + k^\mu e_{\mu},\quad
		e_{\mu\nu}
		\mapsto e_{\mu\nu}
			+ \beta_\mu k_\nu
			+ \beta_\nu k_\mu,\quad
		e_\mu
		\mapsto e_\mu + \beta k_\mu
	\end{equation}
	Here $e_{\mu\nu},e_\mu,\beta_\mu,\beta$ are seen as arbitrary gauge parameters. For closed string the result can be obtained by the doubling trick, i.e.\ by introducing anti-holomorphic modes $\tilde{\alpha},\tilde{b},\tilde{c}$ and imposing reality conditions. The result is similar. \qedfull

@@

	For $z\mapsto z + \epsilon(z)$, we have:
	\begin{equation}
		\var{X^\mu}
		= - \epsilon\pd X^\mu
			- \bar{\epsilon}\pdbar X^\mu
			- \frac{\alpha'V^\mu}{2}\,\pqty{
				\pd\epsilon
				+ \pdbar\bar{\epsilon}
			}
	\end{equation}
	Note that the $\alpha'$ term has no dependence on $X$.

	\begin{enumerate}
	\item For simplicity, assume for now $X = X(z)$: holomorphic. Note that the $\alpha'$ term comes from the transformation of \textit{internal} degrees of freedom. We have:
	\begin{gather}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pd\epsilon
			+ \order{\epsilon^2},
%		\simeq -\frac{\alpha' V}{2}\,\pqty{
%			\dv{z'}{z} - 1
%		},\\[.5ex]
%		X'(z') - \frac{\alpha' V}{2}
%		\simeq X(z) - \frac{\alpha' V}{2}\,
%			\dv{z'}{z},
%		\\[1ex]
%		X'(z')
%		\simeq X(z) + \frac{\alpha' V}{2}\,\pqty{
%				1 - \pd w + \order{\pd w}^2
%			},
		\label{eq:dilaton_holomorphic}
	\end{gather}
	This is a first order approximation of the finite transformation $z\mapsto z' = w(z)$.

	To obtain a full expression, notice that for the above transformation to be a \textit{symmetry}, the action should be invariant under $X(z)\mapsto X'(z)$:
	\begin{equation}
		S' = S
		\propto \int \dd[2]{z}
			\pd X^\mu \pdbar X_\mu
		= \int \dd[2]{z'}
			\pd' X'^\mu \pdbar' X'_\mu
%		= \int \dd[2]{z'}
%			\pd' X'^\mu \pdbar' X'_\mu (z',\bar{z}')
	\end{equation}
	Restore the anti-holomorphic component and insert \eqref{eq:dilaton_holomorphic}, then we find that in order to cancel the $\order{\epsilon^2}$ terms, we have to fix:
%	\begin{gather}
%		X'(z',\bar{z}') - \alpha'V
%		\simeq X(z,\bar{z})
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{z'}{z} + \dv{\bar{z}'}{\bar{z}}
%			},\\[1ex]
%		X\longmapsto
%		X'(z,\bar{z})
%		\simeq X\pqty\Big{
%				w^{-1}(z),\bar{w}^{-1}(\bar{z})
%			} + \alpha'V
%			- \frac{\alpha' V}{2}\,\pqty{
%				\dv{w}{z} + \dv{\bar{w}}{\bar{z}}
%			},
%	\end{gather}
	\begin{equation}
		X'(z') - X(z)
		= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \order{\epsilon^3}
		}
	\end{equation}
	The above process can be done order by order, in the end we obtain that\footnote{
		I would like to thank Lucy Smith for helpful discussions. 
	}:
	\begin{equation}
	\begin{aligned}
		X'(z',\bar{z}') - X(z,\bar{z})
		&= -\frac{\alpha' V}{2}\,\pqty{
			\pd\epsilon
			- \frac{1}{2}\,(\pd\epsilon)^2
			+ \frac{1}{3}\,(\pd\epsilon)^2
			- \cdots
		} + \pqty{\mrm{conjugate}} \\
		&= -\frac{\alpha' V}{2}\,
			\ln (1 + \pd\epsilon)
		+ \pqty{\mrm{conjugate}} \\[.5ex]
		&= -\frac{\alpha' V}{2}\,
			\ln \pqty{
				\dv{z'}{z}
				\dv{\bar{z}'}{\bar{z}}
			}
	\end{aligned}
	\end{equation}

	\item Perform the usual Noether's procedure on the free boson action, and we have:
	\begin{equation}
		\var{\mcal{L}}
		\propto \frac{1}{\alpha'} \pqty{
				\pd \var{X}^\mu \pdbar X_\mu
				+ \pd X^\mu \pdbar \var{X}_\mu
			}
		\sim \pdbar \epsilon \pqty{
			V^\mu \pd^2 X^\mu
			- \frac{1}{\alpha'}
				\pd X^\mu \pdbar X_\mu
		}
	\end{equation}
	Here we've plugged in the holomorphic part of $\var{X}^\mu$, used integration by parts to move $\pdbar$ before $\epsilon$, and collected the $\pdbar\epsilon$ coefficients. This gives:
	\begin{equation}
		T(z) = - \frac{1}{\alpha'}\,\normorder{
				\pd X^\mu \pdbar X_\mu\!
			} + V^\mu \pd^2 X^\mu
	\end{equation}
